%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
    {} % Affiliation/role
    {International Conference} % Organization/group
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Camera-driven Representation Learning for Unsupervised Domain Adaptive Person Re-identification. \textit{ICCV} 2023.\\ Geon Lee, \textbf{Sanghoon Lee}, Dohyung Kim, Younghoon Shin, Yongsang Yoon, Bumsub Ham.}\\
        \item {Decomposed Knowledge Distillation for Class-incremental Semantic Segmentation. \textit{NeurIPS} 2022.\\ Donghyeon Baek, Youngmin Oh, \textbf{Sanghoon Lee}, Junghyup Lee, Bumsub Ham.}\\
        \item {OIMNet++: Prototypical Normalization and Localization-aware Learning for Person Search. \textit{ECCV} 2022.\\ \textbf{Sanghoon Lee}, Youngmin Oh, Donghyeon Baek, Junghyup Lee, Bumsub Ham.}\\
        \item {Learning by Aligning: Visible-Infrared Person Re-identification using Cross-Modal Correspondences. \textit{ICCV} 2021.\\ Hyunjong Park*, \textbf{Sanghoon Lee*}, Junghyup Lee, Bumsub Ham.}\\
        \item {HVPR: Hybrid Voxel-Point Representation for Single-stage 3D Object Detection. \textit{CVPR} 2021.\\ Jongyoun Noh, \textbf{Sanghoon Lee}, Bumsub Ham.}\\
      \end{cvitems}
    }

\cventry
    {} % Affiliation/role
    {International Journal} % Organization/group
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {PLoPS: Localization-Aware Person Search with Prototypical Normalization. \textit{Pattern Recognition} 2024.\\ \textbf{Sanghoon Lee}, Youngmin Oh, Donghyeon Baek, Junghyup Lee, Bumsub Ham.}
      \end{cvitems}
    }



\end{cventries}